Topological order in the quantum dimer-pentamer model

### 2015-09-28 qdpm_paper.tex
a few minor chages. Gap estimates should be more correct
better images

@@

@@

    \begin{table*}[htpb]
    \setlength\tabcolsep{0.3cm}
        \centering
        \caption{$\Delta \tau = 150$}
        \label{tab:label}
        \begin{tabular}{l l l l l}
            \hline\hline
         L            		& 8x8                               		& 12x12                            		& 16x16					& 18x18 \\ 
            \hline                                                                                                                           
         frac 1.0     	&                                       		&                                  		&                                    		&  \\
            \hline                                                                                                                           
         Dimer        	&  $ 3(1) \times 10^{-2}$        	& $ 1.43(3) \times 10^{-2}$	& $0.81(2)\times 10^{-2}$  	& \\
         $Z_2$ origin 	&  $ 0.787?(5)\times 10^{-2} $ 	& $ 0.344? (1)\times 10^{-2}$ 	& $0.198? (4)\times 10^{-2} $ 	&  \\
         $Z_3$ origin 	&  NA                                   	& NA                               		& NA                                  	& \\
            \hline                                                                                                                         
         frac 0.9     	&                                       		&                                  		&                                     		&  \\
            \hline                                                                                                                          
         Dimer origin 	&  $ 0.419(1)\times 10^{-2} $    	& $ 0.406(2)\times 10^{-2} $ 	& $0.429(1)\times 10^{-2} $   	&  $ 0.405(2)\times 10^{-2} $\\
         $Z_2$ origin 	&  $ 0.216?(2)\times 10^{-2} $ 	& $ 0.141?(1)\times 10^{-2} $ 	& $0.129?(2)\times 10^{-2} $	&  $ 0.126?(2)\times 10^{-2} $\\
         $Z_3$ origin 	&  $ 0.346?(4)\times 10^{-2} $ 	& $ 0.348(1)\times 10^{-2} $ 	& $0.359?(4)\times 10^{-2} $	&  $ 0.355?(3)\times 10^{-2}$\\
            \hline                                                                                                                          
         frac 0.5     	&                                       		&                                   		&                                    		& \\
            \hline                                                                                                                          
         Dimer origin 	&                                       		& $ 2.075(9)\times 10^{-2} $ 	& $2.05(1) \times 10^{-2}$		&  $ $ \\
         $Z_2$ origin 	&                                       		& $ 0.615?(2)\times 10^{-2} $ 	& $0.614?(3)\times 10^{-2} $	&  $ $ \\
         $Z_3$ origin 	&                                       		& $ 1.939(2)\times 10^{-2} $ 	& $1.927(2)\times 10^{-2} $	&  $ $  
        \end{tabular}
    \end{table*}

>>>>

\begin{figure}[htpb]
    \centering
    \includegraphics[width=0.8\linewidth]{example_local_constraints.pdf}
    \caption{Clockwise from the upper left panel we show an example of a QDM with constraints: one
    dimer, two dimers, an even number of dimers, and and odd number of dimers touching each vertex.}
    \label{fig:example_local_constraints}
\end{figure}

@@

            \begin{figure}[htpb]
                \centering
                \includegraphics[width=0.8\linewidth]{u1_wind_qdpm.pdf}
                \caption{The $U(1)$ winding number as measured in the QDPM on a $16\times16$ lattice
                with a dimer to pentamer move fraction (need a name for this fraction HERE) of 0.5.}
                \label{fig:u1_wind_qdpm}
            \end{figure}

@@

%    \begin{table*}[htpb]
%    \setlength\tabcolsep{0.3cm}
%        \centering
%        \caption{$\Delta \tau = 150$}
%        \label{tab:label}
%        \begin{tabular}{l l l l l}
%            \hline\hline
%         L            		& 8x8                               		& 12x12                            		& 16x16					& 18x18 \\ 
%            \hline                                                                                                                           
%         frac 1.0     	&                                       		&                                  		&                                    		&  \\
%            \hline                                                                                                                           
%         Dimer        	&  $ 3(1) \times 10^{-2}$        	& $ 1.43(3) \times 10^{-2}$	& $0.81(2)\times 10^{-2}$  	& \\
%         $Z_2$ origin 	&  $ 0.787?(5)\times 10^{-2} $ 	& $ 0.344? (1)\times 10^{-2}$ 	& $0.198? (4)\times 10^{-2} $ 	&  \\
%         $Z_3$ origin 	&  NA                                   	& NA                               		& NA                                  	& \\
%            \hline                                                                                                                         
%         frac 0.9     	&                                       		&                                  		&                                     		&  \\
%            \hline                                                                                                                          
%         Dimer origin 	&  $ 0.419(1)\times 10^{-2} $    	& $ 0.406(2)\times 10^{-2} $ 	& $0.429(1)\times 10^{-2} $   	&  $ 0.405(2)\times 10^{-2} $\\
%         $Z_2$ origin 	&  $ 0.216?(2)\times 10^{-2} $ 	& $ 0.141?(1)\times 10^{-2} $ 	& $0.129?(2)\times 10^{-2} $	&  $ 0.126?(2)\times 10^{-2} $\\
%         $Z_3$ origin 	&  $ 0.346?(4)\times 10^{-2} $ 	& $ 0.348(1)\times 10^{-2} $ 	& $0.359?(4)\times 10^{-2} $	&  $ 0.355?(3)\times 10^{-2}$\\
%            \hline                                                                                                                          
%         frac 0.5     	&                                       		&                                   		&                                    		& \\
%            \hline                                                                                                                          
%         Dimer origin 	&                                       		& $ 2.075(9)\times 10^{-2} $ 	& $2.05(1) \times 10^{-2}$		&  $ $ \\
%         $Z_2$ origin 	&                                       		& $ 0.615?(2)\times 10^{-2} $ 	& $0.614?(3)\times 10^{-2} $	&  $ $ \\
%         $Z_3$ origin 	&                                       		& $ 1.939(2)\times 10^{-2} $ 	& $1.927(2)\times 10^{-2} $	&  $ $  
%        \end{tabular}
%    \end{table*}

    \begin{table*}[htpb]
    \setlength\tabcolsep{0.3cm}
        \centering
        \caption{$\Delta \tau = 250$}
        \label{tab:label}
        \begin{tabular}{l l l l}
            \hline\hline
                        & Dimer                 & $Z_2$ double ($L/2$)  &  $Z_3$ single (origin)     \\   
            \hline
            frac 1.0    &  &  & \\
            $8\times8$  & $3.(3)\times10^{-2}$  &                       &                            \\
            $12\times12$& $1.4(5)\times10^{-2}$ &                       &                            \\
            $16\times16$&                       &                       &                            \\
            $18\times18$&                       &                       &                            \\
            \hline
            frac 0.9    &  &  & \\
            $8\times8$  & $0.35(6)\times10^{-2}$&$0.102(1)\times10^{-2}$& $0.306(3)\times10^{-2}$     \\
            $12\times12$& $0.35(7)\times10^{-2}$&$0.25(5)\times10^{-2}$ & $0.316(4)\times10^{-2}$    \\
            $16\times16$& $0.35(7)\times10^{-2}$&$0.36(3)\times10^{-2}$ & $0.316(8)\times10^{-2}$    \\
            $18\times18$&                       &                       &                            \\
            \hline
            frac 0.5    &  &  & \\
            $8\times8$  & $1.0(6)\times10^{-2}$ &$0.05(5)\times10^{-2}$ & $1.7(1)\times10^{-2}$     \\
            $12\times12$& $1.5(7)\times10^{-2}$ &                       & $1.9(7)\times10^{-2}$      \\
            $16\times16$&                       &                       &                            \\
            $18\times18$&                       &                       &                            \\
        \end{tabular}
    \end{table*}
